### 2017-09-21 icde/sec-exp.tex

To alleviate the issue of citation missing in \aminer, we added citations by title matching  based on \magdata, and the finally total number of citations is is 14.26 million. These datasets were further cleaned by deleting self-citations and citations from old articles to new ones, which accounted for (0.1\%, 0.8\%, 0.4\%) of the total citations on (\aan, \aminer, \magdata), respectively.
%from old articles to more recent ones
%These datasets were further cleaned by detecting citation cycles and removing those edges violating the temporal order if any.

@@

\noindent
(2) \fcita assumes that scholarly articles with more citations are of higher importance.
%
However, the number of entire citations is obviously biased to old articles. Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this only estimates of future impacts of articles, not at the concerned time. For a fair ranking benchmark, we propose to use both past and future citations with the same period of time \wrt\ the concerned time, such that the number of citations within these two periods reveals the importance of articles at the concerned time.
%
We hence divided each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remain part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
%
%
Moreover, articles in the same pair were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same year, similar to~\cite{Wang16TIST}.
We used all pairs (around 50,000) for \aan, and randomly chose 300,000 pairs for both \aminer and \magdata.

@@

\stitle{Exp-2: Effectiveness with \fcita}.
%\subsubsection{Exp-2: Effectiveness with \fcita}
In the second set of tests, we used ground-truth \fcita to evaluate the effectiveness.
%All algorithms produced results based on articles in ranking data.
Aggregating parameters were selected as follows: $(\alpha, \beta, \gamma)$ = $(0.7, 0.1,$ $0.2)$ for \futurerank, $(a_{i1}, a_{i2}, a_{i3})$ = $(0.3, 0.6, 0.1)$ for \hhgrank ($i\in[1, 3]$), and $(\alpha, \beta)$ = $(0.8, 0.1)$ for \ensemblerank.
%Here the citation component contributed most in \ensemblerank, since \fcita is based on citation information.
To evaluate the effectiveness of ranking in different scenarios, we varied three factors in our tests: the splitting year $Y_s$, the number $T_p$ of published years of articles, and the difference $dif$ of future citation counts.
%
Given $Y_s$, $T_p$ and $dif$, we only used article pairs whose articles were published within $[Y_s - T_p, Y_s)$ and the difference of future citation counts was equal to or larger than $dif$ to test the \PairAcc.
% no earlier than $T_p$ years before $Y_s$

@@

%varying difference of future citation count in benchmark
\etitle{Exp-2.3}.
%\stitle{Exp-2.3}.
To evaluate the effectiveness of ranking \wrt\ {\em the difference of future citations},
we varied the difference $dif$ of future citation counts from 1 to 7, while fixed $Y_s$ to default values of three datasets and $T_i=+\infty$. The results of \PairAcc are reported in Figs.~\ref{exp-aan-fcdiff}, \ref{exp-aminer-fcdiff} and \ref{exp-mag-fcdiff}.

@@

\stitle{Exp-3: Efficiency}.
%\subsubsection{Exp-3: Efficiency}
In the third set of tests, we evaluated the efficiency of our algorithms.
%
We compared our algorithms with \powtwprscc and \powensemble, which were the same to \twprscc and \batensemble except using power method for TWPageRank computation, and with algorithms \futurerank and \hhgrank.
Here \pagerank was omitted due to its effectiveness.
%
We varied the splitting year $Y_s$ from 2009 to 2016 and tested the running time on both \aminer and \magdata.
%
For incremental algorithms, base and update parts consisted of data before 2008 and within $[2008, Y_s)$, respectively.
%And the incremental ratio evaluated by the size of data was 0.11, 0.25, 0.39, 0.55, 0.73, 0.93, 1.14 and 1.30 for $Y_s\in[2009,2016]$.
%
The results of running time are reported in Fig.~\ref{exp-time}, where the red markers $\Box$ in dashed lines mean that \hhgrank ran out of memory.
%The results on the large data \magdata are reported in Fig.~\ref{exp-time}, where red markers \marked{$\Box$} in dashed line mean \hhgrank ran out of memory, and the results on \aminer are left in~\cite{SARank-full}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

To alleviate the issue of citation missing in \aminer, we added citations by title matching  based on \magdata, and the finally total number of citations is 14.26 million. These datasets were further cleaned by deleting self-citations and citations from old articles to new ones, which accounted for (0.1\%, 0.8\%, 0.4\%) of the total citations on (\aan, \aminer, \magdata), respectively.
%from old articles to more recent ones
%These datasets were further cleaned by detecting citation cycles and removing those edges violating the temporal order if any.

@@

\noindent
(2) \fcita assumes that scholarly articles with more citations are of higher importance.
%
However, the number of entire citations is obviously biased to old articles. Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this only estimates future impacts of articles, not at the concerned time. For a fair ranking benchmark, we propose to use both past and future citations with the same period of time \wrt\ the concerned time, such that the number of citations within these two periods reveals the importance of articles at the concerned time.
%
We hence divided each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remaining part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
%
%
Moreover, articles in the same pair were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same year, similar to~\cite{Wang16TIST}.
We used all pairs (around 50,000) for \aan, and randomly chose 300,000 pairs for both \aminer and \magdata.

@@

\stitle{Exp-2: Effectiveness with \fcita}.
%\subsubsection{Exp-2: Effectiveness with \fcita}
In the second set of tests, we used ground-truth \fcita to evaluate the effectiveness.
%All algorithms produced results based on articles in ranking data.
Aggregating parameters were selected as follows: $(\alpha, \beta, \gamma)$ = $(0.7, 0.1, 0.2)$ for \futurerank, $(a_{i1}, a_{i2}, a_{i3})$ = $(0.3, 0.6, 0.1)$ for \hhgrank ($i\in[1, 3]$), and $(\alpha, \beta)$ = $(0.8, 0.1)$ for \ensemblerank.
%Here the citation component contributed most in \ensemblerank, since \fcita is based on citation information.
To evaluate the effectiveness of ranking in different scenarios, we varied three factors in our tests: the splitting year $Y_s$, the number $T_p$ of published years of articles, and the difference $dif$ of past and future citation counts.
%
Given $Y_s$, $T_p$ and $dif$, we only used article pairs whose articles were published within $[Y_s - T_p, Y_s)$ and the difference of past and future citation counts was equal to or larger than $dif$ to test the \PairAcc.
% no earlier than $T_p$ years before $Y_s$

@@

%varying difference of future citation count in benchmark
\etitle{Exp-2.3}.
%\stitle{Exp-2.3}.
To evaluate the effectiveness of ranking \wrt\ {\em the difference of past and future citations},
we varied the difference $dif$ of past and future citation counts from 1 to 7, while fixed $Y_s$ to default values of three datasets and $T_i=+\infty$. The results of \PairAcc are reported in Figs.~\ref{exp-aan-fcdiff}, \ref{exp-aminer-fcdiff} and \ref{exp-mag-fcdiff}.

@@

\stitle{Exp-3: Efficiency}.
%\subsubsection{Exp-3: Efficiency}
In the third set of tests, we evaluated the efficiency of our algorithms.
%
We compared our algorithms with \powtwprscc and \powensemble, which were the same to \twprscc and \batensemble except using power method for TWPageRank computation, and with algorithms \futurerank and \hhgrank.
Here \pagerank was omitted due to its effectiveness.
%
We varied the splitting year $Y_s$ from 2009 to 2015 and tested the running time on both \aminer and \magdata.
%
For incremental algorithms, base and update parts consisted of data before 2008 and within $[2008, Y_s)$, respectively.
%And the incremental ratio evaluated by the size of data was 0.11, 0.25, 0.39, 0.55, 0.73, 0.93, 1.14 and 1.30 for $Y_s\in[2009,2016]$.
%
The results of running time are reported in Fig.~\ref{exp-time}, where the red markers $\Box$ in dashed lines mean that \hhgrank ran out of memory.
%The results on the large data \magdata are reported in Fig.~\ref{exp-time}, where red markers \marked{$\Box$} in dashed line mean \hhgrank ran out of memory, and the results on \aminer are left in~\cite{SARank-full}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Impacts of TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
